---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shinidraw

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of shinidraw is to ...

## Installation

You can install the development version of shinidraw like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Run the app

You can launch the app with:

```r
shinidraw::run_app()
```

## About

You're reading the doc about version : `r pkgload::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

Here are the test & coverage results :

```{r}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("shinipsum")
```

```{r}
covr::package_coverage()
```

## Code of Conduct

Please note that the shinidraw project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
